\documentclass[11pt,a4paper]{article}
\date{}

\usepackage{titlesec}
\usepackage{titling}
\usepackage{hyperref}
\usepackage[margin=2cm]{geometry}

\renewcommand{\familydefault}{\sfdefault}

\titleformat{\section}
{\rmfamily\Huge}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\bfseries\large}
{}
{0.0em}
{}

\titleformat{\subsubsection}[runin]
{\bfseries\large}
{$\bullet$}
{0.5em}
{}

\renewcommand{\maketitle}{
\begin{center}
{\huge\bfseries
\theauthor}

\vspace{.25em}

\thetitle

\vspace{.25em}

contact@pouriamokhtari.ir
\end{center}
}

\begin{document}
\title{Site Reliability Engineering R\'esum\'e}
\author{Pouria Mokhtari}

\maketitle
\section{Experience}

\subsection{Medeschain --- Site Reliability Engineering}
August 2021 --- present

\begin{itemize}
	\setlength\itemsep{0.1em}
	\item{Maintained a private Gitlab instance for CI/CD with dedicated build servers.}
	\item{Configured VMware ESXI virtual machines to be used as Kubernetes nodes.}
	\item{Worked with Kubernetes and Docker, extending clusters and load-balancing for new products.}
	\item{Installed and maintained a Kubernetes Dashboard to visualize cluster status.}
	\item{Configured the ELK stack for container monitoring + log management.}
	\item{Used Ansible to setup multiple instances of different services.}
	\item{Used Terraform to manage and reproduce infrastructure across platforms.}
\end{itemize}

\subsection{Agah E-Commerce --- Site Reliability Engineering}
August 2020 ---  August 2021
\begin{itemize}
	\setlength\itemsep{0.1em}
	\item{Configuration of Gitlab CI/CD setup with build servers and automatic testing and deployment.}
	\item{Configured Envoy as gateway and reverse-proxy.}
	\item{Traefik Docker container-based service configuration and load-balancing.}
	\item{Implemented performance monitoring with Prometheus.}
	\item{Used Docker and docker-compose to maintain 30+ services.}
	\item{Created build and containerization scripts for many projects based on frontend and backend web-development frameworks and libraries. Including Vue, Angular, React, Nextjs, ROR, ExpressJS, Laravel, ASP.NET core and... .}
	\item{Maintained and hardened serveral cryptocurrency node servers with their respective JSON-RPC APIs.}
	\item{Implemented interval-based and synchronization backup solutions.}
\end{itemize}

\subsection{Karama --- System Administration}
March 2019 --- July 2020
\begin{itemize}
	\setlength\itemsep{0.1em}
	\item{Load-balancing implementation with nginx.}
	\item{Used Docker and docker-compose to maintain 10+ API services.}
	\item{Implemented setup scripts and configurations with Chef.}
	\item{Used Jenkins to implement a simple CI/CD workflow.}
	\item{Linux server setup, hardening and maintainance (Debian, CentOS).}
	\item{Installed and configured OpenBSD-based storage server.}
	\item{Maintained Email Servers (SMTP, IMAP).}
	\item{Worked with Proxmox to create and Manage Virtual machines.}
\end{itemize}

\section{Education}

\subsection {Urmia University of Technology --- Bachelors Degree}
September 2018 --- July 2022

\section{Skills}

\section{Contact}

\subsubsection{Phone:}
+98 935 761 1522
\subsubsection{Website:}
\url{https://pouriamokhtari.ir}

\subsubsection{Github:}
\url{https://github.com/pouriamokhtari}

\end{document}
